Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-15 write-ups/PLDI/paper.tex
Tweaks.

\ADComment{Refer back to nonfunctional requirements section, \mysec\ref{sec:nonfunctional}.}

@@

\ADComment{Can we remark a bit more on the outliers?}

@@

\paragraph{Performance} \ADComment{I don't think it's clear how overhead is computed; we need to make it clear that it is a slow-down.  Let's discuss.}
\myfiglong\ref{fig:performance} reports, for the Iris GPU, the overhead brought by the scheduling of
non-cooperative kernels over the cooperative kernel execution time (geometric mean over all applications and inputs), along with the period (aritmetic mean over all applications
and inputs) at which non-cooperative kernels can be scheduled.
The results for the other GPUs are similar and are graphed in Appendix~\ref{appendix:extraperformance} (supplementary material).
 We show
results for the three workloads listed in
\mysec~\ref{sec:sizingnoncoop}. The two gray horizontal lines in the
period graph correspond to the period goals of the workloads: the higher
(resp. lower) line corresponds to a period of 70ms (resp. 40ms) for the
light (resp. medium and heavy) workload.

@@

Still the heavy
workloads meet their period (by allocating all-but-one workgroup for
non-cooperative kernels), incurring a slow down of less than 1.4$\times$ on average. Light
and medium workloads meet their period with only a negligable overhead
of the cooperative kernel (less than a 1.03$\times$ slowdown on average).

Overall we are encouraged by our experimental findings, which provide a lower bound on potential performance of our coperative kernels model: implementing the model natively, with device-specific runtime support, could only improve performance and responsiveness compared with that of our megakernel-based prototype.

>>>>

@@

@@

\paragraph{Performance} 
\myfiglong\ref{fig:performance} reports, for the Iris GPU, the overhead brought by the scheduling of
non-cooperative kernels over the cooperative kernel execution time.  This is the slowdown associated with running the cooperative kernel in the presence of multitasking, vs.\ running the cooperative kenrel in isolation (geometric mean over all applications and inputs).  We also show the period at which non-cooperative kernels can be scheduled (aritmetic mean over all applications
and inputs).
The results for the other GPUs are similar and are graphed in Appendix~\ref{appendix:extraperformance} (supplementary material).
 We show
results for the three workloads listed in
\mysec~\ref{sec:sizingnoncoop}. The two gray horizontal lines in the
period graph correspond to the period goals of the workloads: the higher
(resp. lower) line corresponds to a period of 70ms (resp. 40ms) for the
light (resp. medium and heavy) workload.

@@

Still, the heavy
workloads meet their period (by allocating all-but-one workgroup for
non-cooperative kernels), incurring a slow down of less than 1.4$\times$ on average. Light
and medium workloads meet their period with only a negligable overhead
of the cooperative kernel (less than a 1.03$\times$ slowdown on average).

Overall we are very encouraged by these experimental findings, especially since they provide a lower bound on potential performance of our coperative kernels model. Implementing the model natively, with device-specific runtime support, could only improve performance and responsiveness compared with that of our megakernel-based prototype.
